### 2012-07-03 inst/examples/Reed.Rmd
bias table updated with lots more replicates

``` {r  find_dp_opt }
opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime=25, xT=0, 
                     profit, delta=0.05, reward=0)
````

@@

``` {r policyfn_plot}
q1 <- qplot(x_grid, x_grid - x_grid[opt$D[,1]], xlab="stock size", ylab="escapement") + 
geom_point(aes(x,y), data=data.frame(x=opt$S, y=opt$S), col="red")
q1
````

>>>>

``` {r  find_dp_opt }
opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, profit, delta, reward=0)
````

## Compare to Clark (noise-free)

``` {r  }
pdfn2 <- function(P, s){
  dunif(P, 1 - s, 1 + s)
}
SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, 0, pdfn2)
````

``` {r  find_dp_opt }
det <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, profit, delta, reward=0)
````

@@

``` {r policyfn_plot}
require(reshape2)
policies <- melt(data.frame(tsock=x_grid, S = x_grid[opt$D[,1]], D = x_grid[det$D[,1]]), id="stock")

q1 <- ggplot(policies, aes(x_grid, x_grid - value)) + xlab("stock size") + ylab=("escapement") 
q1
````

### 2012-07-03 inst/examples/bias_table.Rmd
updated bigger grid
bias table updated with lots more replicates

``` {r }
xmin <- 0
xmax <- 1.5 * K
grid_n <- 100
````

@@

``` {r simfn, rerun=TRUE} 
simulatereps <- function(opt, pars){
  sims <- lapply(1:100, function(i){
    ForwardSimulate(f, pars, x_grid, h_grid, x0 = K, opt$D, z_g, z_m, z_i, profit)
  })
  sims
}
````

>>>>

``` {r }
xmin <- 0
xmax <- 2.5 * K
grid_n <- 200
````

@@

``` {r simfn, rerun=TRUE} 
simulatereps <- function(opt, pars){
  sims <- lapply(1:5000, function(i){
    ForwardSimulate(f, pars, x_grid, h_grid, x0 = K, opt$D, z_g, z_m, z_i, profit)
  })
  sims
}
````
